Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-05 S3_run_simulations_EE_not_last.Rmd
fix nr of cores

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- min(c(200L, parallel::detectCores() - 1))

@@

timeout <- 24 * 60 * 60 # a Day

>>>>

```{r}
## Identify number of CPU cores available for parallel computing,
## note: using a large number may lead RAM to max out, so you may have to adjust
## that according to your infrastructure:
nb_cores <- 50

@@

timeout <- 1 * 60 * 60 # an Hour
